---
title: " "
format:
  html:
    self-contained: true
    toc: true
    toc-title: "Studies"
    toc-depth: 1
    theme: none
    include-in-header:
      text: |
        <link href="https://fonts.googleapis.com/css2?family=Fraunces:ital,opsz,wght@0,9..144,400;0,9..144,700;1,9..144,400&family=Figtree:wght@300;400;600&display=swap" rel="stylesheet">
        <style>
          :root { --sand:#f5f0e8; --sand-dark:#e8e0d0; --ink:#2c2418; --ink-mid:#5a4d3e;
            --ink-light:#8a7d6b; --terra:#c47a4a; --terra-light:#e8a87c; --sage:#7aab85;
            --slate:#5b8fa8; --purple:#7b3294; --white:#fff; --border:#ddd5c8; }
          body { font-family:'Figtree',sans-serif; background:var(--sand); color:var(--ink);
                 max-width:960px; margin:0 auto; padding:3rem 1.5rem; font-size:18px; }
          h1 { font-family:'Fraunces',serif; font-size:2.6rem; line-height:1.08;
               letter-spacing:-0.03em; border:none; margin-bottom:0.6rem; }
          h1 em { font-style:italic; color:var(--terra); }
          h2 { font-family:'Fraunces',serif; font-size:1.5rem; margin-top:3rem; margin-bottom:0.6rem;
               color:var(--ink); padding-top:2rem; border-top:2px solid var(--border); }
          h3 { font-family:'Fraunces',serif; font-size:1.15rem; color:var(--ink-mid);
               margin-top:1.5rem; margin-bottom:0.4rem; }
          p,li { font-size:1.05rem; line-height:1.85; color:var(--ink-mid); font-weight:300; }
          strong { color:var(--ink); font-weight:600; }
          .note { background:var(--white); border-left:3px solid var(--sage);
                  border-radius:0 12px 12px 0; padding:1rem 1.2rem; margin:1rem 0;
                  font-size:1rem; color:var(--ink-mid); line-height:1.65; }
          .study-num { font-family:'Fraunces',serif; font-size:3rem; font-weight:700;
                       color:var(--sand-dark); float:left; margin-right:0.6rem; line-height:1; }
          table { width:100%; border-collapse:collapse; font-size:0.92rem; margin:0.8rem 0; }
          th { text-align:left; font-size:0.72rem; font-weight:600; text-transform:uppercase;
               letter-spacing:0.07em; color:var(--ink-light); padding:0.55rem 0.6rem;
               border-bottom:2px solid var(--border); background:var(--sand-dark); }
          td { padding:0.45rem 0.6rem; border-bottom:1px solid var(--border); color:var(--ink-mid); }
          tr:hover td { background:var(--sand-dark); }
          .leaflet-container { border-radius:12px !important; }
          .footer { margin-top:3.5rem; padding-top:1.2rem; border-top:1px solid var(--border);
                    font-size:0.85rem; color:var(--ink-light); text-align:center; }
          .quarto-title { display:none; }
          #TOC { font-size:0.85rem; }
          #TOC a { color:var(--ink-mid); text-decoration:none; }
          #TOC a:hover { color:var(--terra); }
          .nav-tabs { border-bottom:2px solid var(--border); margin-bottom:1rem; }
          .nav-tabs .nav-link { font-family:'Figtree',sans-serif; font-size:0.9rem;
            color:var(--ink-light); border:none; padding:0.5rem 1rem; }
          .nav-tabs .nav-link.active { color:var(--terra); border-bottom:2px solid var(--terra);
            font-weight:600; }
          .tab-content { min-height:200px; }
          .js-plotly-plot { border-radius:12px; }
        </style>
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(sf)
library(leaflet)
library(ggplot2)
library(plotly)

e1 <- new.env(); if (file.exists("ws_1_equity.RData")) load("ws_1_equity.RData", envir = e1)
e2 <- new.env(); if (file.exists("ws_2_heat.RData")) load("ws_2_heat.RData", envir = e2)
e3 <- new.env(); if (file.exists("ws_3_monsoon.RData")) load("ws_3_monsoon.RData", envir = e3)
e4 <- new.env(); if (file.exists("ws_4_projections.RData")) load("ws_4_projections.RData", envir = e4)
e5 <- new.env(); if (file.exists("ws_5_health.RData")) load("ws_5_health.RData", envir = e5)
if (!exists("bg_sf", envir = e1) && file.exists("workspace.RData")) load("workspace.RData", envir = e1)

hl <- highlightOptions(weight = 2, color = "#2c2418", fillOpacity = 0.9)
pal4 <- c("#2c7bb6", "#abd9e9", "#fee090", "#d73027")

## Choropleth map helper
cmap <- function(sf_data, var, title, popup_vars, popup_labs, pal_colors = pal4) {
  vals <- sf_data[[var]]
  pal <- colorNumeric(pal_colors, domain = vals, na.color = "#ccc")
  pop <- sapply(seq_len(nrow(sf_data)), function(i) {
    bits <- sapply(seq_along(popup_vars), function(j) {
      paste0(popup_labs[j], ": <strong>", round(sf_data[[popup_vars[j]]][i], 2), "</strong>")
    })
    paste0("<div style='font-family:Figtree;font-size:0.9rem;line-height:1.6'>",
           paste(bits, collapse = "<br>"), "</div>")
  })
  leaflet(sf_data, width = "100%", height = "440px") |>
    addProviderTiles("CartoDB.Positron") |>
    addPolygons(fillColor = ~pal(vals), fillOpacity = 0.75, weight = 0.5,
                color = "#fff", popup = pop, highlightOptions = hl) |>
    addLegend(pal = pal, values = vals, title = title, position = "bottomright", opacity = 0.8)
}
```

```{r header}
#| output: asis
cat('<h1>Evaporative Cooling in <em>Tucson</em></h1>')
cat('<p>Swamp coolers are everywhere in Tucson. Cheap to run, great in dry heat, but they fail when humidity rises. <strong>We mapped where they are for the first time.</strong> Five studies, one dataset.</p>')
```


# 1 -- Equity

<span class="study-num">1</span> **Who depends on evaporative cooling?** Lower-income neighborhoods, neighborhoods with more renters, older housing, and higher minority proportions all have significantly higher evaporative cooler prevalence.

::: {.panel-tabset}

## Maps

```{r p1-maps, results='asis'}
bg1 <- e1$bg; sf1 <- e1$bg_sf
sf1 <- st_make_valid(sf1)
pvars <- c("evap_prop", "med_income", "pct_minority", "pct_renter", "med_year_built")
plabs <- c("Evap. prevalence", "Income ($)", "Minority (%)", "Renter (%)", "Year built")

## Evap prevalence map with all variables in popup
cmap(sf1, "evap_prop", "Evap. cooling", pvars, plabs)
```

```{r p1-sociodem}
#| output: asis
cat("Switch maps below to explore sociodemographic patterns.\n\n")
```

```{r p1-income}
cmap(sf1, "med_income", "Median income ($)", pvars, plabs, rev(pal4))
```

```{r p1-minority}
cmap(sf1, "pct_minority", "Minority (%)", pvars, plabs)
```

## Relationships

```{r p1-scatter}
bg1$evap_pct <- bg1$evap_prop * 100
bg1$min_pct <- bg1$pct_minority * 100
bg1$rent_pct <- bg1$pct_renter * 100

p <- ggplot(bg1, aes(x = min_pct, y = evap_pct,
                      text = paste0("Evap: ", round(evap_pct,1), "%",
                                    "<br>Income: $", formatC(med_income, big.mark=","),
                                    "<br>Minority: ", round(min_pct,0), "%",
                                    "<br>Renter: ", round(rent_pct,0), "%"))) +
  geom_point(alpha = 0.5, color = "#5b8fa8", size = 2) +
  geom_smooth(method = "loess", se = TRUE, color = "#d73027", fill = "#fc8d59", alpha = 0.15) +
  theme_minimal(base_size = 12) +
  labs(x = "Minority (%)", y = "Evap. cooler prevalence (%)")

ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8", family = "Figtree")))
```

```{r p1-scatter2}
p2 <- ggplot(bg1, aes(x = med_income / 1000, y = evap_pct,
                       text = paste0("Evap: ", round(evap_pct,1), "%",
                                     "<br>Income: $", formatC(med_income, big.mark=","),
                                     "<br>Minority: ", round(min_pct,0), "%"))) +
  geom_point(alpha = 0.5, color = "#5b8fa8", size = 2) +
  geom_smooth(method = "loess", se = TRUE, color = "#d73027", fill = "#fc8d59", alpha = 0.15) +
  theme_minimal(base_size = 12) +
  labs(x = "Median income ($K)", y = "Evap. cooler prevalence (%)")

ggplotly(p2, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
```

## Covenants

```{r p1-cov}
#| output: asis
or_fish <- e1$or_fish; cov_in <- e1$cov_in; cov_out <- e1$cov_out
cat(sprintf('::: {.note}\nNeighborhoods inside historically covenanted areas have **%sx higher odds** of high evaporative cooler prevalence (p = %s). Average prevalence inside: **%s%%**. Outside: **%s%%**.\n:::\n',
            round(or_fish$estimate, 1), signif(or_fish$p.value, 3),
            round(mean(cov_in) * 100, 1), round(mean(cov_out) * 100, 1)))
```

```{r p1-covmap}
pal_cov <- colorFactor(c("#e8e0d0", "#7b3294"), domain = c(0, 1))
pop_cov <- sprintf("<div style='font-family:Figtree;font-size:0.9rem'>Evap: <strong>%s%%</strong><br>Covenanted: <strong>%s</strong><br>Income: $%s</div>",
  round(sf1$evap_prop * 100, 1), ifelse(sf1$covenant == 1, "Yes", "No"),
  formatC(sf1$med_income, format = "d", big.mark = ","))

leaflet(sf1, width = "100%", height = "420px") |>
  addProviderTiles("CartoDB.Positron") |>
  addPolygons(fillColor = ~pal_cov(covenant), fillOpacity = 0.7,
              weight = 0.5, color = "#fff", popup = pop_cov, highlightOptions = hl) |>
  addLegend(colors = c("#e8e0d0", "#7b3294"), labels = c("No", "Yes"),
            title = "Covenanted", position = "bottomright", opacity = 0.8)
```

## LISA clusters

```{r p1-lisa}
sf1$lisa_cluster <- bg1$lisa_cluster
lisa_pal <- colorFactor(c("#d7191c", "#fdae61", "#abd9e9", "#2c7bb6", "grey85"),
                         levels = c("High-High", "High-Low", "Low-High", "Low-Low", "Not significant"))
pop_lisa <- sprintf("<div style='font-family:Figtree;font-size:0.9rem'>Cluster: <strong>%s</strong><br>Evap: %s%%</div>",
  sf1$lisa_cluster, round(sf1$evap_prop * 100, 1))

leaflet(sf1, width = "100%", height = "420px") |>
  addProviderTiles("CartoDB.Positron") |>
  addPolygons(fillColor = ~lisa_pal(lisa_cluster), fillOpacity = 0.75,
              weight = 0.5, color = "#fff", popup = pop_lisa, highlightOptions = hl) |>
  addLegend(pal = lisa_pal, values = ~lisa_cluster, title = "LISA cluster",
            position = "bottomright", opacity = 0.8)
```

:::


# 2 -- Heat island

<span class="study-num">2</span> **Do the hottest neighborhoods also have the most swamp coolers?** We overlaid evaporative cooler prevalence with summer maximum temperature to identify double-exposure hotspots.

::: {.panel-tabset}

## Temperature map

```{r p2-tmax}
if (exists("bg", envir = e2)) {
  bg2 <- e2$bg; sf2 <- st_as_sf(bg2); sf2 <- st_make_valid(sf2)
  if (is.na(st_crs(sf2))) sf2 <- st_set_crs(sf2, 4326)
  cmap(sf2, "mean_tmax", "Summer tmax (C)",
       c("evap_prop", "mean_tmax", "med_income", "pct_minority"),
       c("Evap. prevalence", "Tmax (C)", "Income ($)", "Minority (%)"))
} else { cat('<div class="note">Run Script 2 first.</div>') }
```

## NDVI map

```{r p2-ndvi}
if (exists("bg", envir = e2) && "mean_ndvi" %in% colnames(e2$bg) && !all(is.na(e2$bg$mean_ndvi))) {
  cmap(sf2, "mean_ndvi", "Mean NDVI",
       c("mean_ndvi", "mean_tmax", "evap_prop", "med_income"),
       c("NDVI", "Tmax (C)", "Evap. prevalence", "Income ($)"),
       c("#f0e6c8", "#c6d69e", "#78b560", "#2a7f2a"))
} else { cat('<div class="note">NDVI data not available. Run Script 2 with NDVI raster.</div>') }
```

## Double exposure

```{r p2-bivar}
if (exists("bg", envir = e2) && "bi_cluster" %in% colnames(e2$bg)) {
  sf2$bi_cluster <- bg2$bi_cluster
  bi_pal <- colorFactor(c("#d7191c", "#fdae61", "#abd9e9", "#2c7bb6", "grey85"),
    levels = c("High evap / Hot", "High evap / Cool", "Low evap / Hot", "Low evap / Cool", "Not significant"))
  pop_bi <- sprintf("<div style='font-family:Figtree;font-size:0.9rem'>Cluster: <strong>%s</strong><br>Evap: %s%% | Tmax: %s C</div>",
    sf2$bi_cluster, round(sf2$evap_prop * 100, 1), round(sf2$mean_tmax, 1))
  leaflet(sf2, width = "100%", height = "440px") |>
    addProviderTiles("CartoDB.Positron") |>
    addPolygons(fillColor = ~bi_pal(bi_cluster), fillOpacity = 0.75,
                weight = 0.5, color = "#fff", popup = pop_bi, highlightOptions = hl) |>
    addLegend(pal = bi_pal, values = ~bi_cluster, title = "Bivariate LISA",
              position = "bottomright", opacity = 0.8)
} else { cat('<div class="note">Run Script 2 first.</div>') }
```

## Scatter

```{r p2-scatter}
if (exists("bg", envir = e2)) {
  bg2$evap_pct <- bg2$evap_prop * 100
  p <- ggplot(bg2, aes(x = mean_tmax, y = evap_pct,
                        text = paste0("Evap: ", round(evap_pct,1), "%",
                                      "<br>Tmax: ", round(mean_tmax,1), " C",
                                      "<br>Income: $", formatC(med_income, big.mark=",")))) +
    geom_point(alpha = 0.5, color = "#5b8fa8", size = 2) +
    geom_smooth(method = "loess", se = TRUE, color = "#d73027", fill = "#fc8d59", alpha = 0.15) +
    theme_minimal(base_size = 12) +
    labs(x = "Mean summer tmax (C)", y = "Evap. prevalence (%)")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
}
```

:::


# 3 -- Monsoon failure

<span class="study-num">3</span> **When do swamp coolers stop working?** Evaporative coolers lose effectiveness when humidity rises. We quantified how often this happens using 6 years of hourly weather data.

::: {.panel-tabset}

## Failure heatmap

```{r p3-heatmap}
if (exists("heatmap_data", envir = e3)) {
  hd <- e3$heatmap_data
  p <- ggplot(hd, aes(x = doy, y = hour, fill = fail_prop,
                       text = paste0("DOY: ", doy, " Hour: ", hour,
                                     "<br>Temp: ", round(mean_temp, 1), " F",
                                     "<br>RH: ", round(mean_rh, 1), "%",
                                     "<br>Failure prob: ", round(fail_prop, 2)))) +
    geom_tile() +
    scale_fill_gradientn(colors = c("#f7f7f7", "#fc8d59", "#b30000"), name = "Failure\nprobability") +
    scale_y_continuous(breaks = seq(0, 23, 4)) +
    theme_minimal(base_size = 12) +
    theme(panel.grid = element_blank()) +
    labs(x = "Day of year", y = "Hour")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
} else { cat('<div class="note">Run Script 3 first.</div>') }
```

## Compound exposure map

```{r p3-map}
if (exists("bg", envir = e3) && "compound_exposure" %in% colnames(e3$bg)) {
  bg3 <- e3$bg; sf3 <- st_as_sf(bg3)
  if (is.na(st_crs(sf3))) sf3 <- st_set_crs(sf3, 4326)
  sf3 <- st_make_valid(sf3)
  cmap(sf3, "compound_exposure", "Compound\nexposure",
       c("compound_exposure", "evap_prop", "med_income", "pct_minority"),
       c("Compound exposure", "Evap. prevalence", "Income ($)", "Minority (%)"))
} else { cat('<div class="note">Run Script 3 first.</div>') }
```

## Annual failure days

```{r p3-annual}
if (exists("daily", envir = e3)) {
  at <- aggregate(failure_day ~ year, data = e3$daily, FUN = sum)
  colnames(at)[2] <- "failure_days"
  p <- ggplot(at, aes(x = year, y = failure_days,
                       text = paste0(year, ": ", failure_days, " days"))) +
    geom_col(fill = "#d73027", alpha = 0.7, width = 0.6) +
    geom_hline(yintercept = mean(at$failure_days), linetype = "dashed", color = "grey40") +
    theme_minimal(base_size = 12) +
    labs(x = "Year", y = "Failure days (May-Sep)")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
}
```

## Demographics

```{r p3-table}
p3_t2 <- here::here("results", "P3_Table2_demographics_by_exposure.csv")
if (file.exists(p3_t2)) knitr::kable(read.csv(p3_t2), row.names = FALSE,
  caption = "High vs. low compound exposure neighborhoods")
```

:::


# 4 -- Climate projections

<span class="study-num">4</span> **What happens as Tucson gets hotter?** Using CMIP6 climate projections (SSP2-4.5 and SSP5-8.5), we estimated how cooler failure days will change through the 2060s.

::: {.panel-tabset}

## Projections

```{r p4-fan}
if (exists("ribbon_df", envir = e4) && exists("baseline_failure_days", envir = e4)) {
  rd <- e4$ribbon_df; bfd <- e4$baseline_failure_days
  rd$ssp_label <- ifelse(rd$ssp == "ssp245", "SSP2-4.5", "SSP5-8.5")

  p <- ggplot(rd, aes(x = period_year, text = paste0("Period: ", period_year,
                        "<br>Scenario: ", ssp_label,
                        "<br>Median: ", round(median, 1),
                        "<br>Range: ", round(lo, 1), " - ", round(hi, 1)))) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = ssp_label), alpha = 0.2) +
    geom_line(aes(y = median, color = ssp_label), linewidth = 1) +
    geom_hline(yintercept = bfd, linetype = "dashed", color = "grey40") +
    scale_fill_manual(values = c("SSP2-4.5" = "#2c7bb6", "SSP5-8.5" = "#d73027")) +
    scale_color_manual(values = c("SSP2-4.5" = "#2c7bb6", "SSP5-8.5" = "#d73027")) +
    theme_minimal(base_size = 12) +
    labs(x = "", y = "Failure days per summer", fill = "", color = "")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
} else { cat('<div class="note">Run Script 4 first.</div>') }
```

## Threshold crossing

```{r p4-bars}
if (exists("crossing_summary", envir = e4)) {
  cs <- e4$crossing_summary
  cs_future <- cs[cs$ssp != "observed", ]
  cs_future$ssp_label <- ifelse(cs_future$ssp == "ssp245", "SSP2-4.5", "SSP5-8.5")
  cs_future$period <- factor(cs_future$period, levels = c("near", "mid", "far"))
  baseline_pct <- cs$pct_above[cs$ssp == "observed"]

  p <- ggplot(cs_future, aes(x = period, y = pct_above, fill = ssp_label,
                              text = paste0(ssp_label, " ", period,
                                            "<br>Above threshold: ", pct_above, "%",
                                            "<br>Newly above: ", pct_newly_above, "%"))) +
    geom_col(position = "dodge", width = 0.6, alpha = 0.8) +
    geom_hline(yintercept = baseline_pct, linetype = "dashed", color = "grey40") +
    scale_fill_manual(values = c("SSP2-4.5" = "#2c7bb6", "SSP5-8.5" = "#d73027")) +
    scale_x_discrete(labels = c("2030s", "2040s", "2060s")) +
    theme_minimal(base_size = 12) +
    labs(x = "", y = "% block groups above threshold", fill = "")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
}
```

## Projected exposure map

```{r p4-map}
if (exists("bg", envir = e4) && "exposure_ssp585_far" %in% colnames(e4$bg)) {
  bg4 <- e4$bg; sf4 <- st_as_sf(bg4)
  if (is.na(st_crs(sf4))) sf4 <- st_set_crs(sf4, 4326)
  sf4 <- st_make_valid(sf4)
  cmap(sf4, "exposure_ssp585_far", "Projected exposure\n(2060s SSP5-8.5)",
       c("exposure_current", "exposure_ssp585_far", "evap_prop", "med_income"),
       c("Current exposure", "2060s exposure", "Evap. prevalence", "Income ($)"))
} else { cat('<div class="note">Run Script 4 first.</div>') }
```

## Current vs future

```{r p4-current}
if (exists("bg", envir = e4) && "exposure_current" %in% colnames(e4$bg)) {
  cmap(sf4, "exposure_current", "Current exposure",
       c("exposure_current", "exposure_ssp585_far", "evap_prop"),
       c("Current", "2060s SSP5-8.5", "Evap. prevalence"))
}
```

:::


# 5 -- Health outcomes

<span class="study-num">5</span> **Do heat-related EMS calls cluster in neighborhoods with more swamp coolers?** We linked heat-related health data to cooling type, temperature, and demographics to test whether inadequate cooling translates to worse health outcomes.

::: {.panel-tabset}

## Call rate map

```{r p5-map}
if (exists("bg", envir = e5) && "call_rate" %in% colnames(e5$bg)) {
  bg5 <- e5$bg; sf5 <- st_as_sf(bg5)
  if (is.na(st_crs(sf5))) sf5 <- st_set_crs(sf5, 4326)
  sf5 <- st_make_valid(sf5)
  cmap(sf5, "call_rate", "Call rate\n(per 1000 days)",
       c("call_rate", "evap_prop", "med_income", "pct_minority"),
       c("Call rate", "Evap. prevalence", "Income ($)", "Minority (%)"))
} else { cat('<div class="note">Run Script 5 first.</div>') }
```

## Calls vs evap

```{r p5-scatter}
if (exists("bg", envir = e5) && "call_rate" %in% colnames(e5$bg)) {
  bg5$evap_pct <- bg5$evap_prop * 100
  p <- ggplot(bg5, aes(x = evap_pct, y = call_rate,
                        text = paste0("Evap: ", round(evap_pct, 1), "%",
                                      "<br>Call rate: ", round(call_rate, 2),
                                      "<br>Income: $", formatC(med_income, big.mark = ",")))) +
    geom_point(alpha = 0.5, color = "#5b8fa8", size = 2) +
    geom_smooth(method = "lm", se = TRUE, color = "#d73027", fill = "#fc8d59", alpha = 0.15) +
    theme_minimal(base_size = 12) +
    labs(x = "Evap. cooler prevalence (%)", y = "Heat-related call rate (per 1000 days)")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
}
```

## By quartile

```{r p5-quartile}
if (exists("bg", envir = e5) && "call_rate" %in% colnames(e5$bg)) {
  bg5$evap_q <- cut(bg5$evap_prop,
                     breaks = quantile(bg5$evap_prop, probs = 0:4/4),
                     labels = c("Q1 (lowest)", "Q2", "Q3", "Q4 (highest)"),
                     include.lowest = TRUE)
  p <- ggplot(bg5, aes(x = evap_q, y = call_rate, fill = evap_q,
                        text = paste0("Quartile: ", evap_q,
                                      "<br>Call rate: ", round(call_rate, 2)))) +
    geom_boxplot(alpha = 0.7, outlier.size = 0.8) +
    scale_fill_manual(values = c("#abd9e9", "#fee090", "#fc8d59", "#d73027"), guide = "none") +
    theme_minimal(base_size = 12) +
    labs(x = "Evap. prevalence quartile", y = "Call rate (per 1000 days)")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
}
```

## Failure days

```{r p5-failure}
if (exists("daily_calls", envir = e5) && "failure_day" %in% colnames(e5$daily_calls)) {
  dc <- e5$daily_calls
  dc$label <- ifelse(dc$failure_day == 1, "Failure day", "Non-failure day")
  p <- ggplot(dc, aes(x = label, y = calls, fill = label,
                       text = paste0(label, "<br>Calls: ", calls))) +
    geom_boxplot(alpha = 0.7, outlier.size = 0.8) +
    scale_fill_manual(values = c("Non-failure day" = "#2c7bb6", "Failure day" = "#d73027"), guide = "none") +
    theme_minimal(base_size = 12) +
    labs(x = "", y = "Daily heat-related calls (city-wide)")
  ggplotly(p, tooltip = "text") |> layout(hoverlabel = list(bgcolor = "#2c2418", font = list(color = "#f5f0e8")))
}
```

## Model results

```{r p5-tables}
p5_t2 <- here::here("results", "P5_Table2_NB_regression.csv")
p5_t4 <- here::here("results", "P5_Table4_interaction_model.csv")
if (file.exists(p5_t2)) {
  cat("### Negative binomial regression\n\n")
  knitr::kable(read.csv(p5_t2), row.names = FALSE,
    caption = "Predictors of heat-related call counts (IRR = incidence rate ratio)")
}
if (file.exists(p5_t4)) {
  cat("\n\n### Interaction: failure day x evap prevalence\n\n")
  knitr::kable(read.csv(p5_t4), row.names = FALSE,
    caption = "Does the health impact of cooler-failure days amplify in high-evap neighborhoods?")
}
```

:::


# About

This is the first household-level spatial dataset of evaporative cooler adoption in a US city. What you see here are block group summaries, not individual household data. Five studies examining cooling equity, urban heat exposure, monsoon vulnerability, climate adaptation, and health outcomes in Tucson.

::: {.footer}
Data Diversity Lab, University of Arizona. `r Sys.Date()`.
:::
