---
title: " "
format:
  html:
    self-contained: true
    toc: false
    theme: none
    include-in-header:
      text: |
        <link href="https://fonts.googleapis.com/css2?family=Fraunces:ital,opsz,wght@0,9..144,400;0,9..144,700;1,9..144,400&family=Figtree:wght@300;400;600&display=swap" rel="stylesheet">
        <script src="https://cdn.plot.ly/plotly-2.27.0.min.js"></script>
        <style>
          :root {
            --sand:       #f5f0e8;
            --sand-dark:  #e8e0d0;
            --ink:        #2c2418;
            --ink-mid:    #5a4d3e;
            --ink-light:  #8a7d6b;
            --terra:      #c47a4a;
            --terra-light:#e8a87c;
            --terra-pale: #f5e0d0;
            --sage:       #7aab85;
            --sage-mist:  #eef7f0;
            --slate:      #5b8fa8;
            --slate-light:#a0c4d4;
            --purple:     #7b3294;
            --white:      #ffffff;
            --border:     #ddd5c8;
          }
          body { font-family: 'Figtree', sans-serif; background: var(--sand); color: var(--ink);
                 max-width: 900px; margin: 0 auto; padding: 3rem 1.5rem; font-size: 18px; }

          h1 { font-family: 'Fraunces', serif; font-size: 2.6rem; line-height: 1.08;
               letter-spacing: -0.03em; border: none; margin-bottom: 0.6rem; color: var(--ink); }
          h1 em { font-style: italic; color: var(--terra); }
          h2 { font-family: 'Fraunces', serif; font-size: 1.6rem; margin-top: 3.5rem;
               margin-bottom: 0.6rem; color: var(--ink); letter-spacing: -0.02em;
               padding-top: 2rem; border-top: 1px solid var(--border); }
          h2 em { font-style: italic; color: var(--sage); }
          p { font-size: 1.05rem; line-height: 1.85; color: var(--ink-mid); font-weight: 300; }
          strong { color: var(--ink); font-weight: 600; }

          .note { background: var(--white); border-left: 3px solid var(--sage);
                  border-radius: 0 12px 12px 0; padding: 1rem 1.2rem; margin: 1rem 0;
                  font-size: 1rem; color: var(--ink-mid); line-height: 1.65; }

          .compare-card { background: var(--white); border: 1.5px solid var(--border);
                  border-radius: 16px; padding: 1.4rem 1.6rem; margin: 1rem 0; }
          .compare-title { font-family: 'Fraunces', serif; font-size: 1.1rem; font-weight: 700;
                           color: var(--ink); margin-bottom: 0.6rem; }
          .compare-row { display: flex; justify-content: space-between; align-items: center;
                         padding: 0.5rem 0; border-bottom: 1px solid var(--border); font-size: 0.95rem; }
          .compare-row:last-child { border-bottom: none; }
          .compare-label { color: var(--ink-light); font-weight: 400; min-width: 100px; }
          .compare-val { font-weight: 600; color: var(--ink); min-width: 70px; text-align: right; }
          .compare-avg { font-weight: 300; color: var(--ink-light); font-size: 0.85rem; min-width: 90px; text-align: right; }
          .bar-bg { flex: 1; height: 8px; background: var(--sand-dark); border-radius: 4px;
                    margin: 0 0.8rem; position: relative; }
          .bar-fill { height: 100%; border-radius: 4px; background: var(--terra-light); }
          .bar-marker { position: absolute; top: -3px; width: 2px; height: 14px;
                        background: var(--ink); border-radius: 1px; }

          table { width: 100%; border-collapse: collapse; font-size: 0.95rem; margin: 0.8rem 0; }
          th { text-align: left; font-size: 0.75rem; font-weight: 600; text-transform: uppercase;
               letter-spacing: 0.07em; color: var(--ink-light); padding: 0.6rem 0.7rem;
               border-bottom: 2px solid var(--border); background: var(--sand-dark); }
          td { padding: 0.5rem 0.7rem; border-bottom: 1px solid var(--border); color: var(--ink-mid); }
          tr:hover td { background: var(--sand-dark); }

          .axis-pick { display: flex; gap: 0.7rem; align-items: center; flex-wrap: wrap;
                       margin-bottom: 1rem; }
          .axis-pick label { font-size: 0.85rem; font-weight: 600; color: var(--ink);
                             text-transform: uppercase; letter-spacing: 0.05em; }
          .axis-pick select { font-family: 'Figtree', sans-serif; font-size: 1rem;
            padding: 0.45rem 0.9rem; border: 1.5px solid var(--border); border-radius: 8px;
            background: var(--white); color: var(--ink); cursor: pointer; }

          .leaflet-container { border-radius: 12px !important; }
          .footer { margin-top: 3.5rem; padding-top: 1.2rem; border-top: 1px solid var(--border);
                    font-size: 0.85rem; color: var(--ink-light); text-align: center; }
        </style>
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
load("workspace.RData")
library(sf)
library(leaflet)
```

```{r header}
#| output: asis
cat('<h1>Evaporative cooling in <em>Tucson</em></h1>')
cat('<p>Swamp coolers are everywhere in Tucson. Cheap to run, great in dry heat, but they fail when humidity rises and they pull unfiltered air inside. <strong>We mapped where they are for the first time.</strong> Scroll down to explore.</p>')
```

```{r helpers}
#| include: false
map_sf <- bg_sf
hl <- highlightOptions(weight = 2, color = "#2c2418", fillOpacity = 0.9)

avg_evap <- round(mean(bg$evap_prop) * 100, 1)
avg_inc  <- round(mean(bg$med_income))
avg_min  <- round(mean(bg$pct_minority) * 100, 0)
avg_rent <- round(mean(bg$pct_renter) * 100, 0)
avg_year <- round(mean(bg$med_year_built))
```

## Find your *neighborhood*

Click any block group. A card will appear below showing how that neighborhood compares to the city average.

```{r main-map}
#| output: asis

map_sf$idx <- seq_len(nrow(map_sf))

pal_evap <- colorNumeric(c("#2c7bb6", "#abd9e9", "#fee090", "#d73027"), domain = map_sf$evap_prop)

pop <- sprintf(
  "<div style='font-family:Figtree,sans-serif;font-size:0.95rem;line-height:1.5'>
   <strong style='font-size:1.15rem'>%s%%</strong> evap. cooling<br>
   Income: $%s | Minority: %s%%<br>
   Renter: %s%% | Built: %s</div>",
  round(map_sf$evap_prop * 100, 1),
  formatC(map_sf$med_income, format = "d", big.mark = ","),
  round(map_sf$pct_minority * 100, 0),
  round(map_sf$pct_renter * 100, 0),
  map_sf$med_year_built)

bg_js <- data.frame(
  evap = round(map_sf$evap_prop * 100, 1),
  income = map_sf$med_income,
  minority = round(map_sf$pct_minority * 100, 0),
  renter = round(map_sf$pct_renter * 100, 0),
  year = map_sf$med_year_built,
  covenant = map_sf$covenant
)
cat(sprintf('<script>var BG = %s;\n', jsonlite::toJSON(bg_js)))
cat(sprintf('var AVG = {evap:%.1f, income:%d, minority:%d, renter:%d, year:%d};\n',
            avg_evap, avg_inc, avg_min, avg_rent, avg_year))
cat('
function showCompare(i) {
  var d = BG[i];
  function bar(val, avg, max) {
    var pct = (val / max * 100).toFixed(0);
    var avgPct = (avg / max * 100).toFixed(0);
    return "<div class=\\"bar-bg\\"><div class=\\"bar-fill\\" style=\\"width:" + pct + "%\\"></div>" +
           "<div class=\\"bar-marker\\" style=\\"left:" + avgPct + "%\\" title=\\"City avg\\"></div></div>";
  }
  var html = "<div class=\\"compare-title\\">This neighborhood vs. Tucson average</div>";
  var rows = [
    {label:"Evap. cooling", val:d.evap+"%", avg:AVG.evap+"%", bar:bar(d.evap, AVG.evap, 100)},
    {label:"Income", val:"$"+d.income.toLocaleString(), avg:"$"+AVG.income.toLocaleString(), bar:bar(d.income, AVG.income, 100000)},
    {label:"Minority", val:d.minority+"%", avg:AVG.minority+"%", bar:bar(d.minority, AVG.minority, 100)},
    {label:"Renter", val:d.renter+"%", avg:AVG.renter+"%", bar:bar(d.renter, AVG.renter, 100)},
    {label:"Year built", val:d.year, avg:AVG.year, bar:""}
  ];
  rows.forEach(function(r) {
    html += "<div class=\\"compare-row\\">" +
      "<span class=\\"compare-label\\">" + r.label + "</span>" +
      r.bar +
      "<span class=\\"compare-val\\">" + r.val + "</span>" +
      "<span class=\\"compare-avg\\">(avg " + r.avg + ")</span></div>";
  });
  if (d.covenant === 1) html += "<div style=\\"margin-top:0.6rem;font-size:0.9rem;color:#7b3294;font-weight:600\\">This area has a historically restrictive covenant.</div>";
  document.getElementById("compare-card").innerHTML = html;
  document.getElementById("compare-card").style.display = "block";
}
</script>')
```

```{r map-render}
leaflet(map_sf, width = "100%", height = "520px") |>
  addProviderTiles("CartoDB.Positron") |>
  addPolygons(fillColor = ~pal_evap(evap_prop),
              fillOpacity = 0.75, weight = 0.5, color = "#fff",
              popup = pop, highlightOptions = hl,
              layerId = ~idx) |>
  addLegend(pal = pal_evap, values = ~evap_prop, title = "Evap. cooling",
            position = "bottomright", opacity = 0.8) |>
  htmlwidgets::onRender("function(el, x) {
    this.on('click', function(e) {
      if (e.layer && e.layer.options && e.layer.options.layerId) {
        showCompare(e.layer.options.layerId - 1);
      }
    });
  }")
```

```{r compare-placeholder}
#| output: asis
cat('<div id="compare-card" class="compare-card" style="display:none"></div>')
```

::: {.note}
The dark mark on each bar is the city average. Click different neighborhoods to compare.
:::

## Explore *relationships*

Pick any two variables. Each dot is a neighborhood. Hover for details.

```{r scatter}
#| output: asis
sdat <- bg[, c("evap_prop", "med_income", "pct_minority", "med_year_built", "pct_renter")]

cat('
<div class="axis-pick">
  <label>X</label>
  <select id="xvar" onchange="updateScatter()">
    <option value="pct_minority" selected>Minority %</option>
    <option value="med_income">Income</option>
    <option value="med_year_built">Year built</option>
    <option value="pct_renter">Renter %</option>
  </select>
  <label>Y</label>
  <select id="yvar" onchange="updateScatter()">
    <option value="evap_prop" selected>Evap. cooling</option>
  </select>
</div>
<div id="scatter-plot" style="width:100%;height:400px;border-radius:12px;"></div>
')

cat(sprintf("<script>\nvar SDATA = %s;\n", jsonlite::toJSON(sdat, dataframe = "columns")))
cat('
var SLABELS = {
  evap_prop: "Evap. cooling prevalence",
  med_income: "Median household income ($)",
  pct_minority: "Minority proportion",
  med_year_built: "Median year built",
  pct_renter: "Renter proportion"
};
function updateScatter() {
  var xv = document.getElementById("xvar").value;
  var yv = document.getElementById("yvar").value;
  var trace = {
    x: SDATA[xv], y: SDATA[yv], mode: "markers",
    marker: { size: 9, color: "#5b8fa8", opacity: 0.5, line: { width: 0.5, color: "#fff" } },
    text: SDATA.evap_prop.map(function(_, i) {
      return "Evap: " + (SDATA.evap_prop[i]*100).toFixed(1) + "%" +
        "<br>Income: $" + SDATA.med_income[i].toLocaleString() +
        "<br>Minority: " + (SDATA.pct_minority[i]*100).toFixed(0) + "%" +
        "<br>Renter: " + (SDATA.pct_renter[i]*100).toFixed(0) + "%";
    }),
    hoverinfo: "text", type: "scatter"
  };
  var layout = {
    xaxis: { title: { text: SLABELS[xv], font: { size: 14 } }, gridcolor: "#ddd5c8", zeroline: false },
    yaxis: { title: { text: SLABELS[yv], font: { size: 14 } }, gridcolor: "#ddd5c8", zeroline: false },
    font: { family: "Figtree, sans-serif", size: 13, color: "#2c2418" },
    paper_bgcolor: "rgba(0,0,0,0)", plot_bgcolor: "rgba(0,0,0,0)",
    margin: { t: 10, r: 15, b: 60, l: 75 },
    hoverlabel: { bgcolor: "#2c2418", font: { color: "#f5f0e8", family: "Figtree", size: 13 } }
  };
  Plotly.react("scatter-plot", [trace], layout, { displayModeBar: false });
}
document.addEventListener("DOMContentLoaded", function() { updateScatter(); });
</script>')
```

::: {.note}
Try different combinations!
:::

## Neighborhoods by *quartile*

We split all block groups into four groups based on their evaporative cooler prevalence (Q1 = lowest, Q4 = highest).

```{r table1}
t1 <- table1
t1$cell <- paste0(t1$mean, " ± ", t1$se)
t1_wide <- reshape(t1[, c("var_label", "quartile", "cell")],
                   idvar = "var_label", timevar = "quartile", direction = "wide")
colnames(t1_wide) <- gsub("cell\\.", "", colnames(t1_wide))
colnames(t1_wide)[1] <- "Variable"
knitr::kable(t1_wide, row.names = FALSE)
```

::: {.note}
Q4 neighborhoods (highest evaporative cooler prevalence) have substantially lower incomes and higher minority than Q1.
:::

## Covenants and *cooling*

Racially restrictive covenants barred non-white families from buying homes in certain Tucson neighborhoods. They were outlawed decades ago, but their legacy persists in the built environment.

```{r cov-stat}
#| output: asis
cat(sprintf('Neighborhoods inside historically covenanted areas have **%sx higher odds** of high evaporative cooler prevalence (p = %s). Average prevalence inside: **%s%%**. Outside: **%s%%**.',
            round(or_fish$estimate, 1), signif(or_fish$p.value, 3),
            round(mean(cov_in) * 100, 1), round(mean(cov_out) * 100, 1)))
```

```{r covenant-map}
pal_cov <- colorFactor(c("#e8e0d0", "#7b3294"), domain = c(0, 1))

pop_cov <- sprintf(
  "<div style='font-family:Figtree,sans-serif;font-size:0.95rem;line-height:1.5'>
   Evap. cooling: <strong>%s%%</strong><br>
   Covenanted: <strong>%s</strong><br>
   Income: $%s</div>",
  round(map_sf$evap_prop * 100, 1),
  ifelse(map_sf$covenant == 1, "Yes", "No"),
  formatC(map_sf$med_income, format = "d", big.mark = ","))

leaflet(map_sf, width = "100%", height = "420px") |>
  addProviderTiles("CartoDB.Positron") |>
  addPolygons(fillColor = ~pal_cov(covenant),
              fillOpacity = 0.7, weight = 0.5, color = "#fff",
              popup = pop_cov, highlightOptions = hl) |>
  addLegend(colors = c("#e8e0d0", "#7b3294"), labels = c("No", "Yes"),
            title = "Covenanted", position = "bottomright", opacity = 0.8)
```

## *About*

This is the first household-level spatial dataset of evaporative cooler adoption in a US city. What you see here are block group summaries, not individual household data. Part of a series of studies on cooling equity, heat vulnerability, and climate adaptation in Tucson.

::: {.footer}
Website designed by the Data Diversity Lab, University of Arizona. `r Sys.Date()`.
:::
