---
title: " "
format:
  html:
    self-contained: true
    toc: true
    toc-title: "Studies"
    toc-depth: 1
    theme: none
    include-in-header:
      text: |
        <link href="https://fonts.googleapis.com/css2?family=Fraunces:ital,opsz,wght@0,9..144,400;0,9..144,700;1,9..144,400&family=Figtree:wght@300;400;600&display=swap" rel="stylesheet">
        <script src="https://cdn.plot.ly/plotly-2.27.0.min.js"></script>
        <style>
          :root {
            --sand:       #f5f0e8;
            --sand-dark:  #e8e0d0;
            --ink:        #2c2418;
            --ink-mid:    #5a4d3e;
            --ink-light:  #8a7d6b;
            --terra:      #c47a4a;
            --terra-light:#e8a87c;
            --sage:       #7aab85;
            --slate:      #5b8fa8;
            --purple:     #7b3294;
            --white:      #ffffff;
            --border:     #ddd5c8;
          }
          body { font-family: 'Figtree', sans-serif; background: var(--sand); color: var(--ink);
                 max-width: 920px; margin: 0 auto; padding: 3rem 1.5rem; font-size: 18px; }
          h1 { font-family: 'Fraunces', serif; font-size: 2.6rem; line-height: 1.08;
               letter-spacing: -0.03em; border: none; margin-bottom: 0.6rem; }
          h1 em { font-style: italic; color: var(--terra); }
          h2 { font-family: 'Fraunces', serif; font-size: 1.5rem; margin-top: 3rem;
               margin-bottom: 0.6rem; color: var(--ink); letter-spacing: -0.02em;
               padding-top: 2rem; border-top: 2px solid var(--border); }
          h3 { font-family: 'Fraunces', serif; font-size: 1.15rem; color: var(--ink-mid);
               margin-top: 1.5rem; margin-bottom: 0.4rem; }
          p, li { font-size: 1.05rem; line-height: 1.85; color: var(--ink-mid); font-weight: 300; }
          strong { color: var(--ink); font-weight: 600; }
          .note { background: var(--white); border-left: 3px solid var(--sage);
                  border-radius: 0 12px 12px 0; padding: 1rem 1.2rem; margin: 1rem 0;
                  font-size: 1rem; color: var(--ink-mid); line-height: 1.65; }
          .study-num { font-family: 'Fraunces', serif; font-size: 3rem; font-weight: 700;
                       color: var(--sand-dark); float: left; margin-right: 0.6rem;
                       line-height: 1; margin-top: 0.1rem; }
          table { width: 100%; border-collapse: collapse; font-size: 0.92rem; margin: 0.8rem 0; }
          th { text-align: left; font-size: 0.72rem; font-weight: 600; text-transform: uppercase;
               letter-spacing: 0.07em; color: var(--ink-light); padding: 0.55rem 0.6rem;
               border-bottom: 2px solid var(--border); background: var(--sand-dark); }
          td { padding: 0.45rem 0.6rem; border-bottom: 1px solid var(--border); color: var(--ink-mid); }
          tr:hover td { background: var(--sand-dark); }
          img.fig { border-radius: 12px; border: 1px solid var(--border); max-width: 100%; margin: 0.8rem 0; }
          .fig-cap { font-size: 0.88rem; color: var(--ink-light); margin-top: -0.3rem;
                     margin-bottom: 1.2rem; font-style: italic; }
          .compare-card { background: var(--white); border: 1.5px solid var(--border);
                  border-radius: 16px; padding: 1.4rem 1.6rem; margin: 1rem 0; }
          .compare-title { font-family: 'Fraunces', serif; font-size: 1.1rem; font-weight: 700;
                           color: var(--ink); margin-bottom: 0.6rem; }
          .compare-row { display: flex; justify-content: space-between; align-items: center;
                         padding: 0.5rem 0; border-bottom: 1px solid var(--border); font-size: 0.95rem; }
          .compare-row:last-child { border-bottom: none; }
          .compare-label { color: var(--ink-light); font-weight: 400; min-width: 100px; }
          .compare-val { font-weight: 600; color: var(--ink); min-width: 70px; text-align: right; }
          .compare-avg { font-weight: 300; color: var(--ink-light); font-size: 0.85rem; min-width: 90px; text-align: right; }
          .bar-bg { flex: 1; height: 8px; background: var(--sand-dark); border-radius: 4px;
                    margin: 0 0.8rem; position: relative; }
          .bar-fill { height: 100%; border-radius: 4px; background: var(--terra-light); }
          .bar-marker { position: absolute; top: -3px; width: 2px; height: 14px;
                        background: var(--ink); border-radius: 1px; }
          .leaflet-container { border-radius: 12px !important; }
          .axis-pick { display: flex; gap: 0.7rem; align-items: center; flex-wrap: wrap; margin-bottom: 1rem; }
          .axis-pick label { font-size: 0.85rem; font-weight: 600; color: var(--ink);
                             text-transform: uppercase; letter-spacing: 0.05em; }
          .axis-pick select { font-family: 'Figtree', sans-serif; font-size: 1rem;
            padding: 0.45rem 0.9rem; border: 1.5px solid var(--border); border-radius: 8px;
            background: var(--white); color: var(--ink); cursor: pointer; }
          .footer { margin-top: 3.5rem; padding-top: 1.2rem; border-top: 1px solid var(--border);
                    font-size: 0.85rem; color: var(--ink-light); text-align: center; }
          .quarto-title { display: none; }
          #TOC { font-size: 0.85rem; }
          #TOC a { color: var(--ink-mid); text-decoration: none; }
          #TOC a:hover { color: var(--terra); }
          .no-data { background: var(--sand-dark); border-radius: 12px; padding: 1.5rem;
                     text-align: center; color: var(--ink-light); font-size: 0.95rem; margin: 1rem 0; }
        </style>
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(sf)
library(leaflet)

## Load workspaces from each script
e1 <- new.env(); if (file.exists("ws_1_equity.RData")) load("ws_1_equity.RData", envir = e1)
e2 <- new.env(); if (file.exists("ws_2_heat.RData")) load("ws_2_heat.RData", envir = e2)
e3 <- new.env(); if (file.exists("ws_3_monsoon.RData")) load("ws_3_monsoon.RData", envir = e3)
e4 <- new.env(); if (file.exists("ws_4_projections.RData")) load("ws_4_projections.RData", envir = e4)

## Backward compat with old single workspace
if (!exists("bg_sf", envir = e1) && file.exists("workspace.RData")) load("workspace.RData", envir = e1)

bg_sf <- e1$bg_sf; bg <- e1$bg
or_fish <- e1$or_fish; cov_in <- e1$cov_in; cov_out <- e1$cov_out; table1 <- e1$table1

show_fig <- function(f, cap = "") {
  p <- here::here("results", f)
  if (file.exists(p)) {
    cat(sprintf('<img src="../results/%s" class="fig" alt="%s">\n', f, cap))
    if (nzchar(cap)) cat(sprintf('<p class="fig-cap">%s</p>\n', cap))
  } else {
    cat(sprintf('<div class="no-data">%s -- run the corresponding script first.</div>\n', f))
  }
}
show_csv <- function(f, cap = "", cols = NULL) {
  p <- here::here("results", f)
  if (file.exists(p)) {
    d <- read.csv(p); if (!is.null(cols)) d <- d[, intersect(cols, names(d)), drop = FALSE]
    knitr::kable(d, row.names = FALSE, caption = cap)
  } else { cat(sprintf('<div class="no-data">%s -- not yet generated.</div>\n', f)) }
}
hl <- highlightOptions(weight = 2, color = "#2c2418", fillOpacity = 0.9)
```

```{r header}
#| output: asis
cat('<h1>Evaporative Cooling in <em>Tucson</em></h1>')
cat('<p>Swamp coolers are everywhere in Tucson. Cheap to run, great in dry heat, but they fail when humidity rises. <strong>We mapped where they are for the first time.</strong> Four studies, one dataset.</p>')
```


# 1 -- Equity

```{r p1-helpers}
#| include: false
map_sf <- bg_sf
map_sf$idx <- seq_len(nrow(map_sf))
avg_evap <- round(mean(bg$evap_prop) * 100, 1)
avg_inc  <- round(mean(bg$med_income))
avg_min  <- round(mean(bg$pct_minority) * 100, 0)
avg_rent <- round(mean(bg$pct_renter) * 100, 0)
avg_year <- round(mean(bg$med_year_built))
```

<span class="study-num">1</span> **Who depends on evaporative cooling?** Lower-income neighborhoods, neighborhoods with more renters, older housing, and higher minority proportions all have significantly higher evaporative cooler prevalence.

### Explore the map

Use the dropdown to switch between sociodemographic variables. Click any block group to compare it to the city average.

```{r p1-js}
#| output: asis

## Pass block group data to JavaScript
bg_js <- data.frame(
  evap = round(map_sf$evap_prop * 100, 1),
  income = map_sf$med_income,
  minority = round(map_sf$pct_minority * 100, 0),
  renter = round(map_sf$pct_renter * 100, 0),
  year = map_sf$med_year_built,
  covenant = map_sf$covenant)

cat(sprintf('<script>\nvar BG = %s;\n', jsonlite::toJSON(bg_js)))
cat(sprintf('var AVG = {evap:%.1f,income:%d,minority:%d,renter:%d,year:%d};\n',
            avg_evap, avg_inc, avg_min, avg_rent, avg_year))
cat('
function showCompare(i) {
  var d = BG[i];
  function bar(val,avg,max) {
    var pct=Math.min(val/max*100,100).toFixed(0);
    var ap=Math.min(avg/max*100,100).toFixed(0);
    return "<div class=\\"bar-bg\\"><div class=\\"bar-fill\\" style=\\"width:"+pct+"%\\"></div>"+
           "<div class=\\"bar-marker\\" style=\\"left:"+ap+"%\\"></div></div>";
  }
  var h="<div class=\\"compare-title\\">This neighborhood vs. Tucson average</div>";
  [{l:"Evap. cooling",v:d.evap+"%",a:AVG.evap+"%",b:bar(d.evap,AVG.evap,100)},
   {l:"Income",v:"$"+d.income.toLocaleString(),a:"$"+AVG.income.toLocaleString(),b:bar(d.income,AVG.income,120000)},
   {l:"Minority",v:d.minority+"%",a:AVG.minority+"%",b:bar(d.minority,AVG.minority,100)},
   {l:"Renter",v:d.renter+"%",a:AVG.renter+"%",b:bar(d.renter,AVG.renter,100)},
   {l:"Year built",v:d.year,a:AVG.year,b:""}
  ].forEach(function(r){
    h+="<div class=\\"compare-row\\"><span class=\\"compare-label\\">"+r.l+"</span>"+r.b+
       "<span class=\\"compare-val\\">"+r.v+"</span><span class=\\"compare-avg\\">(avg "+r.a+")</span></div>";
  });
  if(d.covenant===1) h+="<div style=\\"margin-top:0.6rem;font-size:0.9rem;color:#7b3294;font-weight:600\\">Historically covenanted area.</div>";
  document.getElementById("cc").innerHTML=h;
  document.getElementById("cc").style.display="block";
}

var MAP1=null;
function updateMap1() {
  if(!MAP1) return;
  var v = document.getElementById("map-var").value;
  var cols = {
    evap_prop:  {pal:["#2c7bb6","#abd9e9","#fee090","#d73027"], key:"evap", div:1, title:"Evap. cooling (%)"},
    med_income: {pal:["#d73027","#fee090","#abd9e9","#2c7bb6"], key:"income", div:1, title:"Median income ($)"},
    pct_minority:{pal:["#2c7bb6","#abd9e9","#fee090","#d73027"], key:"minority", div:1, title:"Minority (%)"},
    pct_renter: {pal:["#2c7bb6","#abd9e9","#fee090","#d73027"], key:"renter", div:1, title:"Renter (%)"},
    med_year_built:{pal:["#d73027","#fee090","#abd9e9","#2c7bb6"], key:"year", div:1, title:"Year built"}
  };
  var c = cols[v];
  var vals = BG.map(function(d){return d[c.key]/c.div;});
  var mn = Math.min.apply(null,vals), mx = Math.max.apply(null,vals);
  MAP1.eachLayer(function(layer){
    if(layer.feature && layer.options && layer.options.layerId) {
      var idx = layer.options.layerId - 1;
      var val = vals[idx];
      var t = (val-mn)/(mx-mn+0.001);
      var r,g,b;
      var p = c.pal;
      if(t<0.33){var s=t/0.33;r=lerp(p[0],p[1],s);}
      else if(t<0.67){var s=(t-0.33)/0.34;r=lerp(p[1],p[2],s);}
      else{var s=(t-0.67)/0.33;r=lerp(p[2],p[3],s);}
      layer.setStyle({fillColor:r});
    }
  });
}
function lerp(c1,c2,t){
  var r1=parseInt(c1.slice(1,3),16),g1=parseInt(c1.slice(3,5),16),b1=parseInt(c1.slice(5,7),16);
  var r2=parseInt(c2.slice(1,3),16),g2=parseInt(c2.slice(3,5),16),b2=parseInt(c2.slice(5,7),16);
  var r=Math.round(r1+(r2-r1)*t),g=Math.round(g1+(g2-g1)*t),b=Math.round(b1+(b2-b1)*t);
  return "#"+((1<<24)+(r<<16)+(g<<8)+b).toString(16).slice(1);
}
</script>')
```

```{r p1-var-select}
#| output: asis
cat('
<div class="axis-pick">
  <label>Map variable</label>
  <select id="map-var" onchange="updateMap1()">
    <option value="evap_prop" selected>Evap. cooler prevalence</option>
    <option value="med_income">Median income</option>
    <option value="pct_minority">Minority %</option>
    <option value="pct_renter">Renter %</option>
    <option value="med_year_built">Year built</option>
  </select>
</div>')
```

```{r p1-map}
pal_evap <- colorNumeric(c("#2c7bb6", "#abd9e9", "#fee090", "#d73027"), domain = map_sf$evap_prop)
pop <- sprintf(
  "<div style='font-family:Figtree,sans-serif;font-size:0.9rem;line-height:1.5'>
   <strong style='font-size:1.1rem'>%s%%</strong> evap. cooling<br>
   Income: $%s | Minority: %s%%<br>
   Renter: %s%% | Built: %s</div>",
  round(map_sf$evap_prop*100,1),
  formatC(map_sf$med_income, format="d", big.mark=","),
  round(map_sf$pct_minority*100,0),
  round(map_sf$pct_renter*100,0),
  map_sf$med_year_built)

leaflet(map_sf, width="100%", height="500px") |>
  addProviderTiles("CartoDB.Positron") |>
  addPolygons(fillColor=~pal_evap(evap_prop), fillOpacity=0.75, weight=0.5,
              color="#fff", popup=pop, highlightOptions=hl, layerId=~idx) |>
  addLegend(pal=pal_evap, values=~evap_prop, title="Evap. cooling",
            position="bottomright", opacity=0.8) |>
  htmlwidgets::onRender("function(el,x){
    MAP1=this;
    this.on('click',function(e){
      if(e.layer&&e.layer.options&&e.layer.options.layerId)
        showCompare(e.layer.options.layerId-1);
    });
  }")
```

```{r p1-card}
#| output: asis
cat('<div id="cc" class="compare-card" style="display:none"></div>')
```

::: {.note}
The dark mark on each bar is the city average. Use the dropdown to recolor the map by income, minority %, renter %, or year built.
:::

### Explore relationships

```{r p1-scatter}
#| output: asis
sdat <- bg[, c("evap_prop","med_income","pct_minority","med_year_built","pct_renter")]
cat('
<div class="axis-pick">
  <label>X</label>
  <select id="xvar" onchange="updateScatter()">
    <option value="pct_minority" selected>Minority %</option>
    <option value="med_income">Income</option>
    <option value="med_year_built">Year built</option>
    <option value="pct_renter">Renter %</option>
    <option value="evap_prop">Evap. cooling</option>
  </select>
  <label>Y</label>
  <select id="yvar" onchange="updateScatter()">
    <option value="evap_prop" selected>Evap. cooling</option>
    <option value="med_income">Income</option>
    <option value="pct_minority">Minority %</option>
    <option value="med_year_built">Year built</option>
    <option value="pct_renter">Renter %</option>
  </select>
</div>
<div id="scatter-plot" style="width:100%;height:400px;border-radius:12px;"></div>')
cat(sprintf("<script>\nvar SDATA=%s;\n", jsonlite::toJSON(sdat, dataframe="columns")))
cat('
var SL={evap_prop:"Evap. cooling prevalence",med_income:"Median household income ($)",
  pct_minority:"Minority proportion",med_year_built:"Median year built",pct_renter:"Renter proportion"};
function updateScatter(){
  var xv=document.getElementById("xvar").value, yv=document.getElementById("yvar").value;
  Plotly.react("scatter-plot",[{
    x:SDATA[xv],y:SDATA[yv],mode:"markers",
    marker:{size:9,color:"#5b8fa8",opacity:0.5,line:{width:0.5,color:"#fff"}},
    text:SDATA.evap_prop.map(function(_,i){
      return "Evap: "+(SDATA.evap_prop[i]*100).toFixed(1)+"%<br>Income: $"+
        SDATA.med_income[i].toLocaleString()+"<br>Minority: "+
        (SDATA.pct_minority[i]*100).toFixed(0)+"%<br>Renter: "+
        (SDATA.pct_renter[i]*100).toFixed(0)+"%";
    }),hoverinfo:"text",type:"scatter"
  }],{
    xaxis:{title:{text:SL[xv],font:{size:14}},gridcolor:"#ddd5c8",zeroline:false},
    yaxis:{title:{text:SL[yv],font:{size:14}},gridcolor:"#ddd5c8",zeroline:false},
    font:{family:"Figtree,sans-serif",size:13,color:"#2c2418"},
    paper_bgcolor:"rgba(0,0,0,0)",plot_bgcolor:"rgba(0,0,0,0)",
    margin:{t:10,r:15,b:60,l:75},
    hoverlabel:{bgcolor:"#2c2418",font:{color:"#f5f0e8",family:"Figtree",size:13}}
  },{displayModeBar:false});
}
document.addEventListener("DOMContentLoaded",function(){updateScatter();});
</script>')
```

### Covenants

```{r p1-cov}
#| output: asis
cat(sprintf('Neighborhoods inside historically covenanted areas have **%sx higher odds** of high evaporative cooler prevalence (p = %s). Average prevalence inside: **%s%%**. Outside: **%s%%**.',
            round(or_fish$estimate,1), signif(or_fish$p.value,3),
            round(mean(cov_in)*100,1), round(mean(cov_out)*100,1)))
```

```{r p1-cov-map}
pal_cov <- colorFactor(c("#e8e0d0","#7b3294"), domain=c(0,1))
pop_cov <- sprintf(
  "<div style='font-family:Figtree,sans-serif;font-size:0.9rem;line-height:1.5'>
   Evap: <strong>%s%%</strong> | Covenanted: <strong>%s</strong><br>Income: $%s</div>",
  round(map_sf$evap_prop*100,1),
  ifelse(map_sf$covenant==1,"Yes","No"),
  formatC(map_sf$med_income,format="d",big.mark=","))

leaflet(map_sf, width="100%", height="380px") |>
  addProviderTiles("CartoDB.Positron") |>
  addPolygons(fillColor=~pal_cov(covenant), fillOpacity=0.7,
              weight=0.5, color="#fff", popup=pop_cov, highlightOptions=hl) |>
  addLegend(colors=c("#e8e0d0","#7b3294"), labels=c("No","Yes"),
            title="Covenanted", position="bottomright", opacity=0.8)
```


# 2 -- Heat island

<span class="study-num">2</span> **Do the hottest neighborhoods also have the most swamp coolers?** We overlaid evaporative cooler prevalence with summer maximum temperature (PRISM 4km) to identify double-exposure hotspots.

```{r p2-figs}
#| output: asis
show_fig("P2_Figure1_bivariate_choropleth.png", "Bivariate choropleth: evaporative cooler prevalence x summer temperature.")
show_fig("P2_Figure2_LISA_double_exposure.png", "Bivariate LISA clusters. Red = high evap / hot (double exposure).")
```

```{r p2-table}
#| output: asis
show_csv("P2_TableS2_hotspot_demographics.csv", "Double-exposure hotspot vs. city-wide demographics")
```

```{r p2-ndvi}
#| output: asis
if (file.exists(here::here("results","P2_Figure3_NDVI_map.png"))) {
  cat("### Vegetation cover\n\n")
  show_fig("P2_Figure3_NDVI_map.png", "Mean NDVI (Landsat 2023-2025). Higher = more tree canopy.")
  show_fig("P2_FigureS3_NDVI_vs_tmax.png", "Less vegetation = hotter neighborhoods.")
}
```

```{r p2-hist}
#| output: asis
show_fig("P2_FigureS2_hotspot_histograms.png", "Hotspot (red) vs. non-hotspot (blue) distributions.")
```


# 3 -- Monsoon failure

<span class="study-num">3</span> **When do swamp coolers stop working?** Evaporative coolers lose effectiveness when humidity rises. We quantified how often this happens during Tucson summers using 6 years of hourly weather data.

```{r p3-figs}
#| output: asis
show_fig("P3_Figure1_heatmap.png", "Hourly conditions across summer. Panel c shows cooler failure probability by day-of-year and hour.")
show_fig("P3_Figure2_compound_exposure_map.png", "Compound exposure by block group (evap prevalence x failure days).")
```

```{r p3-tables}
#| output: asis
show_csv("P3_Table1_failure_climatology.csv", "Cooler failure climatology by season")
show_csv("P3_Table2_demographics_by_exposure.csv", "High vs. low compound exposure neighborhoods")
```

```{r p3-interactive}
## Interactive compound exposure map
if (exists("bg", envir = e3)) {
  bg3 <- e3$bg
  if ("compound_exposure" %in% colnames(bg3)) {
    bg3_sf <- st_as_sf(bg3)
    if (is.na(st_crs(bg3_sf))) bg3_sf <- st_set_crs(bg3_sf, 4326)
    bg3_sf <- st_make_valid(bg3_sf)
    pal3 <- colorNumeric(c("#2c7bb6","#abd9e9","#fee090","#d73027"), domain=bg3$compound_exposure)
    pop3 <- sprintf("<div style='font-family:Figtree,sans-serif;font-size:0.9rem'>Compound exposure: <strong>%.1f</strong><br>Evap: %s%% | Income: $%s</div>",
      bg3$compound_exposure, round(bg3$evap_prop*100,1), formatC(bg3$med_income,format="d",big.mark=","))
    leaflet(bg3_sf, width="100%", height="420px") |>
      addProviderTiles("CartoDB.Positron") |>
      addPolygons(fillColor=~pal3(compound_exposure), fillOpacity=0.75, weight=0.5,
                  color="#fff", popup=pop3, highlightOptions=hl) |>
      addLegend(pal=pal3, values=~compound_exposure, title="Compound\nexposure", position="bottomright", opacity=0.8)
  }
}
```


# 4 -- Climate projections

<span class="study-num">4</span> **What happens as Tucson gets hotter?** Using CMIP6 climate projections (SSP2-4.5 and SSP5-8.5), we estimated how cooler failure days will change through the 2060s and which neighborhoods cross the inadequacy threshold first.

```{r p4-figs}
#| output: asis
show_fig("P4_Figure1_projections.png", "Projected cooler failure days, compound exposure, and threshold crossing.")
```

```{r p4-tables}
#| output: asis
show_csv("P4_Table1_projected_failure_days.csv", "Projected failure days per summer: median [10th-90th percentile]",
         cols=c("ssp","period","label","n_models"))
show_csv("P4_Table2_threshold_crossing.csv", "Block groups exceeding compound exposure threshold by period and scenario")
```

```{r p4-maps}
#| output: asis
show_fig("P4_FigureS1_current_vs_future_maps.png", "Current vs. projected compound exposure (SSP5-8.5, 2060s).")
```

```{r p4-interactive}
## Interactive projection map
if (exists("bg", envir = e4)) {
  bg4 <- e4$bg
  if ("exposure_ssp585_far" %in% colnames(bg4)) {
    bg4_sf <- st_as_sf(bg4)
    if (is.na(st_crs(bg4_sf))) bg4_sf <- st_set_crs(bg4_sf, 4326)
    bg4_sf <- st_make_valid(bg4_sf)
    pal4 <- colorNumeric(c("#2c7bb6","#abd9e9","#fee090","#d73027"), domain=bg4$exposure_ssp585_far)
    pop4 <- sprintf("<div style='font-family:Figtree,sans-serif;font-size:0.9rem'>Current: <strong>%.1f</strong> | 2060s: <strong>%.1f</strong><br>Evap: %s%%</div>",
      bg4$exposure_current, bg4$exposure_ssp585_far, round(bg4$evap_prop*100,1))
    leaflet(bg4_sf, width="100%", height="420px") |>
      addProviderTiles("CartoDB.Positron") |>
      addPolygons(fillColor=~pal4(exposure_ssp585_far), fillOpacity=0.75, weight=0.5,
                  color="#fff", popup=pop4, highlightOptions=hl) |>
      addLegend(pal=pal4, values=~exposure_ssp585_far, title="Projected\nexposure\n(2060s)", position="bottomright", opacity=0.8)
  }
}
```


# About

This is the first household-level spatial dataset of evaporative cooler adoption in a US city. What you see here are block group summaries, not individual household data. Four studies examining cooling equity, urban heat exposure, monsoon vulnerability, and climate adaptation in Tucson.

::: {.footer}
Data Diversity Lab, University of Arizona. `r Sys.Date()`.
:::
